Deep Reinforcement Learning for Conservation Decisions

### 2022-05-31 manuscript/revision_response.Rmd
Missed some comments

Identifying under-explored spaces of the observation-action space is going to be very dependent on the problem. Usually RL practitioners identify under-explored scenarios by either doing extensive testing or visualizing the policy. As the observation-action spaces become large, identifying under-explored regions becomes particularly tough, since it becomes impossible to visualize the policy. When the observation-action space can be easily visualized, then one can rely on their domain knowledge to recognize sub-optimal performance, which is what we have done in both our examples. So the main recommendation is to first try to visualize the policy then perform extensive testing to identify areas of poor exploration.

@@

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. This is something that we alluded to here,

>>>>

This is a great question that we have tried to address in the latest revision,

"Because these simulations rarely reach stock sizes at or above carrying capacity, i.e. larger stock sizes are under-explored, these larger stock sizes show a greater deviation from the optimal policy than we observe at more frequently visited lower stock sizes.
This observation brings up a point that is well worth discussing which is how to best identify and resolve under-explored scenarios.
Usually, RL practitioners identify under-explored scenarios by either doing extensive testing or visualizing the policy, then tweaking the hyperparameters relevant to exploration in hopes of improving the result."

@@

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. This is something that we alluded to in line xxx,
